\subsubsection{Word N-grams}
\label{subsubsec:shingles}

Word N-grams are a sentence analysis technique that consists in dividing the words of a sentence into sequences of $n$ consecutive words. For example, the sentence "the dog barks," can generate the N-grams "the dog" and "dog barks". Word N-grams are useful because they capture \emph{local relationships} between words within a text, so this approach helps identify similar, though not identical, phrases and can \emph{improve search relevance}.
The maximum number of words within an N-gram can be set in the configuration file in \texttt{maxShingleSize}; in our case, we decided to use a maximum of 3 words. Also, we avoided generating unigrams as they do not capture any local relationships within the query.

We then decided to set up a proximity search within each N-gram. The proximity of terms can be used to identify documents in which the search terms occur in a certain \emph{spatial relationship}.
For example, if we are searching for the terms "dog" and "brown" with the proximity of 3 words, we want to find documents in which these two terms appear within a maximum distance of three words from each other. Thus, if a document contains sentences such as "I saw a brown dog in the park" or "The brown dog was running fast", these documents would be considered relevant because the terms "dog" and "brown" are close to each other. In our case, the proximity parameter is set to 5.

Finally, we applied a boost to all word N-grams based on the numer of generated N-grams for a certain query.
